New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-04-21 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
dgnysfgn

classoption       : "man"
output            : papaja::apa6_pdf
# bookdown::word_document2 
---

@@

# merge two data frames by ID 
df_merge <- merge(df_demo_all,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

@@

# exclude cases with no fitbit data
df_demo <- df_demo_all %>% 
  filter(!ID %in% c("126",
                     "132"
                     )
          )

>>>>

classoption       : "man"
output            : bookdown::word_document2 
# papaja::apa6_pdf

---

@@

# merge two data frames by ID 
df_merge <- merge(df_demo_all,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
         )

@@

# exclude cases with no fitbit data
df_demo <- df_demo_all %>% 
  filter(!ID %in% c("126",
                     "132",
                    "236"
                     )
          )

### 2023-04-21 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
dgnysfgn

\begin{tabular}{llllllllll}
\toprule
N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
\midrule
70 & 60.00 & 29.74 & 10.67 & 19.00 & 59.00 & 4.84 & 9.31 & 0.00 & 37.00\\
\bottomrule
\end{tabular}

@@

The sample consisted in total of \emph{N} = 72 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.

The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).

17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.

>>>>

\begin{tabular}{llllllllll}
\toprule
N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
\midrule
78 & 62.82 & NA & NA & NA & NA & NA & NA & NA & NA\\
\bottomrule
\end{tabular}

@@

The sample consisted in total of \emph{N} = 80 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 78 subjects.

The subjects (49 women; 62.82 \%) had a mean age of NA years (\emph{SD} = NA; range: NA-NA) and an average teaching experience of NA years (\emph{SD} = NA; range: NA-NA).

15.38\% of the subjects were (studying to become) teachers for primary school, 69.23\% were (studying to become) teachers for secondary school and 10.26\% were (studying to become) teachers for special education needs.
